Rank Comparison

### 2024-11-26 Code/RankComparison.Rmd
added supplementary analysis

>>>>

# Supplementary Analysis
We are going to see what happens when we pool men's and women's data together.
We sill need to separate by year but will have 3 analyses instead of 6.

### 2019 vs 2022
Data setup
```{r}
men_2019 <- read.csv("../Data/Clusrank2019vs2022.csv")
colnames(men_2019) <- c("Time", "Athlete", "Year", "Event")

women_2019 <- read.csv("../Data/Clusrank2019vs2022Womens.csv")
colnames(women_2019) <- c("Time", "Athlete", "Year", "Event")

women_2019$Athlete <- women_2019$Athlete + 34 #Correction for unique athlete identifier

all_2019 <- rbind(men_2019, women_2019)
```

And now we run the tests
```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = all_2019,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = all_2019,
                method = "ds",
                exact = TRUE, B = 1000000)
```
### 2022 National vs International

Data setup
```{r}
men_2022 <- read.csv("../Data/ClusrankNatvsWorld.csv")
colnames(men_2022) <- c("Time", "Athlete", "Year", "Event")

women_2022 <- read.csv("../Data/ClusrankNatvsWorldWomens.csv")
colnames(women_2022) <- c("Time", "Athlete", "Year", "Event")

women_2022$Athlete <- women_2022$Athlete + 17 #Correction for unique athlete identifier

all_2022 <- rbind(men_2022, women_2022)
```

And now we run the tests.

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = all_2022,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = all_2022,
                method = "ds",
                exact = TRUE, B = 1000000)
```
### 2022 vs 2023

```{r}
men_2023 <- read.csv("../Data/Clusrank2022vs2023.csv")
colnames(men_2023) <- c("Time", "Athlete", "Year", "Event")

women_2023 <- read.csv("../Data/Clusrank2022vs2023Womens.csv")
colnames(women_2023) <- c("Time", "Athlete", "Year", "Event")

women_2023$Athlete <- women_2023$Athlete + 45

all_2023 <- rbind(men_2023, women_2023)
```

Now we run the tests.
```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = all_2023,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = all_2023,
                method = "ds",
                exact = TRUE, B = 1000000)
```
